Headgroup and glycerol backbone structures, and cation binding in bilayers with PS lipids

### 2018-06-29 Manuscript/manuscriptPS.tex
Changed authorship a bit so that only Samuli has a distinct position at the end. + minor corrections

@@

\author{Josef Melcr}
\affiliation{Institute of Organic Chemistry and Biochemistry,
Academy of Sciences of the Czech Republic, 
Prague 6, Czech Republic}

%\author{NMRlipids collaboration \todo{Authorship query to be sent soon.}}
\author{
Amelie Bacle, 
Pavel Buslaev, 
Lukasz Cwiklik, 
Fernando Favela, 
Tiago Ferreira, 
Patrick Fuchs, 
Ivan Gushchin, 
Matti Javanainen, 
Batuhan Kav, 
Jesper Madsen, 
Markus Miettinen, 
Ricky Nencini, 
Chris Papadopoulos, 
Thomas Piggot }
\affiliation{nmrlipids.blogspot.fi}

@@

Our results pave the way for improving the PS lipid parameters for MD simulations. 
We have collected 
 sets of experimental data, which are highly useful in the quality assessment, 
and which are available through the open collaboration platform \url{nmrlipids.blogspot.fi}. 
The pinpointed problematic areas in the models suggest possible directions for corrections.
Such improvements are already in progress \url{https://github.com/jmelcr/ecc_lipids}
following the recent work on PC lipids \cite{melcr18}, 
which use the electronic continuum correction to account for electronic polarization.

>>>>

%\author{Josef Melcr}
%\affiliation{Institute of Organic Chemistry and Biochemistry,
%Academy of Sciences of the Czech Republic, 
%Prague 6, Czech Republic}

%\author{NMRlipids collaboration \todo{Authorship query to be sent soon.}}
\author{
Amelie Bacle, 
Pavel Buslaev, 
Lukasz Cwiklik, 
Fernando Favela, 
Tiago Ferreira, 
Patrick Fuchs, 
Ivan Gushchin, 
Matti Javanainen, 
Batuhan Kav, 
Jesper Madsen, 
Josef Melcr, 
Markus Miettinen, 
Ricky Nencini, 
Chris Papadopoulos, 
Thomas Piggot }
\affiliation{nmrlipids.blogspot.fi}

@@

@@

Our results pave the way for improving the PS lipid parameters for MD simulations. 
We have collected 
 sets of experimental data, which are highly useful in the quality assessment, 
and which are easily accessible through the open collaboration platform \url{nmrlipids.blogspot.fi}. 
The pinpointed problematic areas in the models suggest possible directions for corrections.
Such improvements are already in progress \url{https://github.com/jmelcr/ecc_lipids}
following the recent work on PC lipids \cite{melcr18}, 
which uses the electronic continuum correction to account for electronic polarization.
